---
Title: "Data Wrangling Project R---week3"
---
## 1. Installing packages 
```{r}
install.packages("tidyverse")
```

#### Load tidyverse for use in our notebook
```{r}
library(tidyverse)
```

## 2. Data Importation

### importing the customer CSV file 
```{r}
# a. Importing from a CSV file from URL and loading the entire dataframe.

customer_df <- read_csv("customer.csv")
customer_df
```



## 3. Data Understanding/Exploring Data

#lets preview the first 6 records of the customer dataset
```{r}

head(customer_df)
```

```{r}
#I can quickly check the size of the dataset without displaying additional information

dim(customer_df)
```

```{r}
# I can explore the variable names, datatypes and first few records of the customer dataset.

glimpse(customer_df)

```

##4. Data Cleaning
###4.1 I can check for duplicates
```{r}

customer_df[duplicated(customer_df), ]

```

##4.2 Do we remove the duplicates or pick unique records only? I opt to pick unique records;

```{r}
customer_df[!duplicated(customer_df), ]
customer_clean <- customer_df[!duplicated(customer_df), ]
customer_clean
```
##4.3 Strip the leading and trailing spaces
```{r}
names(customer_clean) <- trimws(names(customer_clean), which = c("both"))
names(customer_clean)
```
##4.4 
# As a standard while working with colunn names we usually use lowercase characters. Thus,
```{r}
names(customer_clean) <- tolower(names(customer_clean))
names(customer_clean)
```
###5. Data analysis
#5.1 I can use a pipe %>%, and then define the column gender to be selected using the `select()` function.
```{r}
customer_clean %>% 
  select(gender)
```
#5.2 I can filter the customer dataset for total charges greater than 5000.
```{r}

filter(customer_clean, totalcharges> 5000)

```
#5.3 I can filter the customer data set to know the churn per gender i.e. which gender did not churn most!
```{r}
#Male--2627rows
#customer_clean[customer_clean$gender == 'Male' & customer_clean$churn == 'No',]

#Female--2551rows
customer_clean[customer_clean$gender == 'Female' & customer_clean$churn == 'No',]
```
###Questions.
1. Which gender churned most?
From point 5.3 above, Female churned most.

2. From question 1 above, what is a possible reason for the churn?
products/offers by the telecom are not crafted for female.

3. what would be my recommendation?
Craft customer retention programs to woe Female and sensitize on the products. 
